The Power of Dependent Reflection

### 2021-07-05 paper.tex
Abstract polishing [take 2]

  Dependent types can be used to ensure programs are correct by construction,
  but they are not available in most
  languages and adding them to an existing language is a difficult task.
  This paper proposes a novel technique to write correct-by-construction
  programs in languages without built-in verification
  capabilities.  This is achieved in three steps.  Firstly, we
  give a shallow embedding of the language (or a subset) into a
  dependently typed language.  Secondly, we write a program
  in that embedding, and we use dependent types to guarantee
  correctness properties of interest.  Thirdly, we
  translate the embedded program back into the original language,
  so that it can be used by the existing compilers and tools.

>>>>

  Most existing programming languages provde very little support to formally
  state and prove properties about programs.  Adding such capabilities is far
  from trivial, as it requires significant reengineering of the existing
  compilers and tools.  This paper proposes a novel technique to write
  correct-by-construction programs in languages without built-in verification
  capabilities, maintaining the ability to use existing tools.
  This is achieved in three steps.  Firstly, we
  give a shallow embedding of the language (or a subset) into a
  dependently typed language.  Secondly, we write a program
  in that embedding, and we use dependent types to guarantee
  correctness properties of interest.  Thirdly, we
  translate the embedded program back into the original language,
  so that it can be used by the existing compilers and tools.
